Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes.

### 2020-05-21 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Almost complete draft. Added new figures

  \section{Choosing Prior Parameters}\label{section:prior_guesses}

  The states identified by the IHMM are heavily influenced by the Gaussian prior
  placed on $\mathbf{c}$ in Equation~\ref{M-eqn:var} of the main text. The 
  entries of $A$ and $\Sigma$ do not vary over a wide range, so the final
  parameters were relatively insensitive to the priors. In order to 
  maximally automate the IHMM procedure, we attempted to parameterize the
  prior on $\mathbf{c}$ in an intelligent way. The prior parameters should
  be chosen such that the mean level of each state lies within a region of 
  reasonable probability of the prior (see Figure~\ref{fig:prior_guesses}).
  In each dimension, we defined the prior mean to lie halfway between the 
  maximum and minimum of each trajectory dimension. To parameterize the 
  prior's variance in each dimension, we defined the maximum and minimum to 
  be 2 standard deviations from the prior mean. Although this approach has 
  worked quite well for the data in this work, it is important to check the 
  results to determine whether further adjustments to the prior might be needed.
%  In Figure TBD, we show the result of a parameterization where the prior
%  parameters of $c$ were poorly chosen. %TODO

@@

>>>>

  \textit{Choosing Prior Parameters}: The states identified by the IHMM are 
  heavily influenced by the Gaussian prior placed on $\mathbf{c}$ in 
  Equation~\ref{M-eqn:var} of the main text. The entries of $A$ and $\Sigma$
  do not vary over a wide range, so the final parameters were relatively 
  insensitive to the priors. In order to maximally automate the IHMM procedure,
  we attempted to parameterize the
  prior on $\mathbf{c}$ in an intelligent way. The prior parameters should
  be chosen such that the mean level of each state lies within a region of 
  reasonable probability of the prior (see Figure~\ref{fig:prior_guesses}).
  In each dimension, we defined the prior mean to lie halfway between the 
  maximum and minimum of each trajectory dimension. To parameterize the 
  prior's variance in each dimension, we defined the maximum and minimum to 
  be 2 standard deviations from the prior mean. Although this approach has 
  worked quite well for the data in this work, it is important to check the 
  results to determine whether further adjustments to the prior might be needed.
%  In Figure TBD, we show the result of a parameterization where the prior
%  parameters of $c$ were poorly chosen. %TODO

@@

  The local number density of heavy atoms surrounding solutes help round out methanol's
  mechanistic picture. Although hydrogen bonding interactions are relatively frequent,
  methanol molecules are unbound by any measurable electrostatic interactions about 
  half or more of the simulation time. Figure~\ref{fig:local_densities} helps to 
  illustrate how the local density of membrane components can aid in solute entrapment.
  When solutes experience long trapping times, the local number density of heavy atoms
  is larger. Even when hydrogen bonds break, surrounding alkane density likely helps 
  keep the solutes in place allowing them to eventually reform. This can happen deep 
  in the tails or close to the monomer head groups. Methanol molecules which experience
  State 3 have by far the smallest local number density which is likely responsible for 
  their mobility, as suggested by the state's large covariance.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{local_densities.pdf}
  \caption{We measured the local number density of heavy atoms surrounding solutes in each
  state. In blue, we plot the local number density experienced by solutes averaged over all
  frames in which the solute occupied the given state. We broke down this overall average 
  number density into number densities measured from instances when the state is occupied 
  for long (orange) versus short(red) dwell time states. We define define `long' dwells times
  as the 50th percentile of all dwell times in the given state, and short as all others. It
  is clear that solutes which experience longer dwells times are also surrounded by more 
  heavy atoms on average.}\label{fig:local_densities}
  \end{figure}
